\documentclass{article}
\title{Artículo De Trump And Tim Hartford}
\author{David Gabriel Corzo Mcmath}
\date{2020-Jan-13 08:47:12}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{fontenc}
\usepackage{pdfpages}
\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{import}
\usepackage{xifthen}
\usepackage{pdfpages}
\usepackage{transparent}
\usepackage{color}
\usepackage{fancyhdr}
\usepackage{lipsum}
\usepackage{sectsty}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{lmodern}
\usepackage{xpatch}
\usepackage{blindtext}
\usepackage{bookmark}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{blindtext}
\usepackage{hyperref}
\usepackage{listing}
\usepackage{spverbatim}
\usepackage{fancyvrb}
\usepackage{fvextra}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{longtable}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle

\section{Tennis ball tarif}
\begin{itemize}
    \item The tennis balls sold tend to have a lot a elasticity. 
    \item Head was the last of the tennis ball manufacturer to move abroad.
    \item Trump imposes tarifs from abroad.
    \item The 25\% tarif will be passed to consumers.
    \item This will affect almost 15\% of the US work force.
    \item Making balls is a specialized process, they need at least 3 years to move back home.
    \item China has bad bussiness practices.
    \item Head expects to loose a lot of money; Wilson's parent company is owned by a chinese person so it will likley be the case that they will stop shiping to the US. 
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tim Hartford}
\begin{itemize}
    \item The DCA found that women's products tend to be more expensive, 6\% across 800 products.
    \item While the DCA could have cherry picked the products could make this study biased.
    \item It does seem to appear that women do pay more.
    \item Gender based markups.
    \item This study can be decieving, womens product in demand is not equivalent to the demand of products of men.
    \item Some nightclubs tend to charge men more than women.
    \item They found that women tend to be more inelastic? If this exists, then women can be more demanding of quality or other qualities en these products, while men are just looking for something cheap.
    \item This doesn't make it alright to charge more to women.
\end{itemize}

































\end{document}
